---
title: "Covid Compare analysis"
output:
  html_notebook:
    code_folding: hide
    theme: lumen
    toc: true
    toc_float: true
---

# Total counts and days to double

```{r message=FALSE, warning=FALSE}
source("../covidcomp_lib.R")
joined <- readJoinJhuData()
comp_data <- joined %>% genCompData()
comp_data %>% plotComps()
```

# Demographics

```{r}
join_wb_country <- function(df, join_data, by=c("Country/Region"="country")) {
  df %>% left_join(
    join_data %>%
      mutate(country = case_when(
        grepl("Bahamas", country) ~ "The Bahamas",
        grepl("Gambia", country) ~ "Gambia, The",
        grepl("Czech", country) ~ "Czechia",
        grepl("Iran", country) ~ "Iran",
        grepl("Ivoire", country) ~ "Cote d'Ivoire",
        grepl("Brunei", country) ~ "Brunei",
        grepl("Republic of Korea", country) ~ "Korea, South",
        grepl("Korea, Rep.", country) ~ "Korea, South",
        grepl("United Kingdom of", country) ~ "United Kingdom",
        grepl("United States", country) ~ "US",
        grepl("Viet", country) ~ "Vietnam",
        grepl("Russia", country) ~ "Russia",
        grepl("Bolivia", country) ~ "Bolivia",
        grepl("Venezuela", country) ~ "Venezuela",
        grepl("Tanzania", country) ~ "Tanzania",
        grepl("Macedonia", country) ~ "North Macedonia",
        grepl("Moldova", country) ~ "Moldova",
        grepl("Egypt", country) ~ "Egypt",
        grepl("Kyrgyz", country) ~ "Kyrgyzstan",
        grepl("Slovak", country) ~ "Slovakia",
        grepl("Vincent", country) ~ "Saint Vincent and the Grenadines",
        grepl("Lucia", country) ~ "Saint Lucia",
        grepl("Martin", country) ~ "Martinique",
        # careful with Congo
        country == "Democratic Republic of the Congo" |
          country == "Congo, Dem. Rep." ~ "Congo (Kinshasa)",
        country == "Congo" | country == "Congo, Rep." ~ "Congo (Brazzaville)",
        TRUE ~ country)),
    by = by)
}
```

## World bank population data

World bank data looks best.  Only two years old.

```{r}
library(wbstats)
demo_data <- joined %>%
  group_by(`Country/Region`) %>%
  summarise_at(vars(confirmed, deaths, recovered), max) %>%
  join_country(
    wb(indicator = "SP.POP.TOTL", startdate = 2018, enddate = 2018) %>%
      rename(population = value) %>%
      select(country, population)) %>%
  mutate(population = case_when(
    `Country/Region` == "Taiwan*" ~ 23780452,
    `Country/Region` == "Cruise Ship" ~ 3711,
    TRUE ~ population)) %>%
  join_country(
    wb(indicator = "SP.POP.65UP.TO.ZS", startdate = 2018, enddate = 2018) %>%
      rename(pct_over_65 = value) %>%
      select(country, pct_over_65)) %>%
  mutate(confirmed_pct = confirmed * 100 / population,
         deaths_pct = deaths * 100 / population,
         recovered_pct = recovered * 100 / population) %>%
  ungroup()

demo_data %>% arrange(desc(deaths_pct), desc(deaths))

demo_data %>%
  arrange(desc(deaths_pct), desc(deaths)) %>%
  head(15) %>%
  mutate(`Country/Region` = reorder(`Country/Region`, desc(deaths_pct))) %>%
  ggplot(aes(confirmed_pct, deaths_pct)) +
  geom_point(aes(color = `Country/Region`)) +
  geom_line(stat = "smooth", method = "lm", alpha = 0.2)

demo_data %>%
  arrange(desc(deaths_pct), desc(deaths)) %>%
  head(15) %>%
  mutate(`Country/Region` = reorder(`Country/Region`, desc(deaths_pct))) %>%
  ggplot(aes(pct_over_65, deaths_pct)) +
  geom_point(aes(color = `Country/Region`)) +
  geom_line(stat = "smooth", method = "lm", alpha = 0.2)

demo_data %>%
  filter(!`Country/Region` %in% c("Cruise Ship", "San Marino", "Martinique")) %>%
  arrange(desc(deaths_pct), desc(deaths)) %>%
  head(15) %>%
  mutate(`Country/Region` = reorder(`Country/Region`, desc(deaths_pct))) %>%
  ggplot(aes(confirmed_pct, deaths_pct)) +
  geom_point(aes(color = `Country/Region`)) +
  geom_line(stat = "smooth", method = "lm", alpha = 0.2)

demo_data %>%
  filter(!`Country/Region` %in% c("Cruise Ship", "San Marino", "Martinique")) %>%
  arrange(desc(deaths_pct), desc(deaths)) %>%
  head(15) %>%
  mutate(`Country/Region` = reorder(`Country/Region`, desc(deaths_pct))) %>%
  ggplot(aes(pct_over_65, deaths_pct)) +
  geom_point(aes(color = `Country/Region`)) +
  geom_line(stat = "smooth", method = "lm", alpha = 0.2)

demo_data %>%
  filter(!`Country/Region` %in% c("Cruise Ship", "San Marino", "Martinique",
                                  "Italy")) %>%
  arrange(desc(deaths_pct), desc(deaths)) %>%
  head(15) %>%
  mutate(`Country/Region` = reorder(`Country/Region`, desc(deaths_pct))) %>%
  ggplot(aes(pct_over_65, deaths_pct)) +
  geom_point(aes(color = `Country/Region`)) +
  geom_line(stat = "smooth", method = "lm", alpha = 0.2)


demo_data %>%
  filter(!`Country/Region` %in% c("Cruise Ship", "San Marino", "Martinique")) %>%
  arrange(desc(deaths_pct), desc(deaths)) %>%
  mutate(`Country/Region` = reorder(`Country/Region`, desc(deaths_pct))) %>%
  ggplot(aes(pct_over_65, deaths_pct)) +
  geom_point(aes(color = `Country/Region`)) +
  geom_line(stat = "smooth", method = "lm", alpha = 0.2) +
  theme(legend.position = "none")
```

# US State-level

```{r}
library(covid19us)
get_states_daily()

state_comp_data <- state_data %>%
  genCompData(geo_level = "Province/State", min_total = 2)
state_comp_data %>% plotComps()
```

## US State testing

```{r}
#library(rvest)
#library(magrittr)
#library(jsonlite)

(state_tests <- url("https://covidtracking.com/api/states/daily") %>%
  jsonlite::fromJSON() %>%
  mutate_at(vars(date), ymd))
```

```{r fig.height=20, fig.width=7}
state_tests %>% select(-total) %>%
  group_by(state) %>%
  summarise(
    positive_test_rate = sum(positive)/((sum(positive) + sum(negative)))) %>%
  arrange(desc(positive_test_rate))

state_tests %>% select(-total) %>%
  group_by(state) %>%
  gather(stat, value, -date, -state)  %>%
  mutate_at(vars(value), as.numeric) %>%
  ggplot(aes(date, value, fill = stat)) +
  geom_bar(stat = "identity") +
  facet_grid(vars(state), scales = "free_y")
```


```{r}
states <- state_data %>%
  left_join(state_abb_map, by = c("Province/State" = "name")) %>%
  left_join(state_tests %>%
              rename_at(vars(-date, -state), list(~ paste0(., "_tests"))),
            by = c("abb" = "state", "date"))
```


```{r fig.height=20, message=FALSE, warning=FALSE}
source("../covidcomp_lib.R")
states %>% select(-abb, -dateChecked_tests) %>%
  genCompData(geo_level = "Province/State", min_total = 2) %>%
  plotComps(min_total = 2, smooth_plots = TRUE, scale_to_fit = TRUE)
```

```{r}
jhu <- fetchPrepJhuData()
```

```{r}
source("../covidcomp_lib.R")
p <- fetchPrepJhuData() %>%
  genCompData() %>% 
  filter(location != "San Marino") %>%
  plotComps()
suppressWarnings(print(p))
```

```{r}
```

```{r}
source("../covidcomp_lib.R")
covtrack <- fetchPrepCovTrackData()
```
```{r}
p <- covtrack %>% genCompData(geo_level = "state", min_stat = "death", min_thresh = 1) %>%
  plotComps()

suppressWarnings(print(p))
```

# Corona Data Scraper project
```{r}
library(jsonlite)
cds_data <- jsonlite::fromJSON("https://coronadatascraper.com/timeseries-byLocation.json")
names(cds_data)
```

```{r}
library(tidyverse)
ita <- cds_data[["ITA"]]
names(ita)
```

```{r}
cds_data %>% head(2)
```
```{r}
sapply(cds_data, "[[", "dates") %>% unlist() %>% names() %>% gsub("^.*\\.", "", .) %>% table() 
sapply(cds_data, names) %>% unlist %>% table %>% sort
```

```{r}
library(tidyverse)
library(jsonlite)
library(lubridate)

cds_data <- jsonlite::fromJSON(
  "https://coronadatascraper.com/timeseries-byLocation.json")

valueOrNA <- function(x) {
  ifelse(!is.null(x), x, NA)
}

getTsMax <- function(cds_loc, metric) {
  suppressWarnings(max(as.numeric(sapply(
    Filter(function(y) {!is.null(y[[metric]])}, cds_loc$dates), "[[", metric))))
}

names(cds_data) %>%
  lapply(FUN = function(x) {
    list(
      name = x,
      country = valueOrNA(cds_data[[x]]$country),
      aggregate = valueOrNA(cds_data[[x]]$aggregate),
      state = valueOrNA(cds_data[[x]]$state),
      population = valueOrNA(cds_data[[x]]$population),
      county = valueOrNA(cds_data[[x]]$county),
      city = valueOrNA(cds_data[[x]]$city),
      max_deaths = getTsMax(cds_data[[x]], "deaths"),
      max_cases = getTsMax(cds_data[[x]], "cases"),
      max_tested = getTsMax(cds_data[[x]], "tested"),
      max_active = getTsMax(cds_data[[x]], "active"),
      max_recovered = getTsMax(cds_data[[x]], "recovered"),
      # deaths_ts = lapply(names(cds_data[[x]]$dates), FUN = function(x) {
      #   c(x = valueOrNA(cds_data[[x]]$dates[[x]]$deaths))
      # }),
      date = list(names(cds_data[[x]]$dates)),
      ts_values = list(cds_data[[x]]$dates))
    }) %>%
  bind_rows() %>% 
  mutate(
    max_deaths = na_if(max_deaths, -Inf),
    max_cases = na_if(max_cases, -Inf),
    max_tested = na_if(max_tested, -Inf),
    max_active = na_if(max_active, -Inf),
    max_recovered = na_if(max_recovered, -Inf)) %>%
  mutate(
    max_deaths_per_capita = max_deaths / population * 1e6,
    max_tested_per_capita = max_tested / population * 1e6,
    max_recovered_per_capita = max_recovered / population * 1e6,
    max_positive_test_rate = max_cases / max_tested) %>%
  unnest(c(date, ts_values)) %>%
  mutate(
    date = ymd(date),
    deaths = unlist(sapply(ts_values, FUN = function(x) {
      return(valueOrNA(x$deaths)) })),
    active = unlist(sapply(ts_values, FUN = function(x) {
      return(valueOrNA(x$active)) })),
    cases = unlist(sapply(ts_values, FUN = function(x) {
      return(valueOrNA(x$cases)) })),
    recovered = unlist(sapply(ts_values, FUN = function(x) {
      return(valueOrNA(x$recovered)) })),
    tested = unlist(sapply(ts_values, FUN = function(x) {
      return(valueOrNA(x$tested)) })),
    growthFactor = unlist(sapply(ts_values, FUN = function(x) {
      return(valueOrNA(x$growthFactor)) })),
    cfr = deaths / cases,
    ptr = cases / tested,
    rr = recovered / cases
    ) %>%
  select(-ts_values) %>%
  gather(stat, value, deaths, active, cases, recovered, tested,
         growthFactor, cfr, ptr, rr) %>%
  mutate(popM = value / population * 1e6) -> cds
```

# NYT data

```{r}
read_csv(url("https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-counties.csv")) %>%
  mutate(cfr = deaths / cases, county = paste(county, "County")) %>%
  mutate(state = unlist(sapply(state, FUN = function(x) { unlist(valueOrNA(state.abb[which(state.name == x)])) }))) %>%
  gather(stat, total, cases, deaths, cfr) %>%
  select(-fips) %>%
  unite(county, county, state, sep = ", ") %>%
  mutate(county = paste0(county, ", USA")) %>%
  left_join(cds %>% filter(country == "USA" & aggregate == "county") %>% select(name, population) %>% unique(), by = c("county" = "name")) %>%
  mutate(popM = total / population * 1e6) %>%
  group_by(county) %>%
  mutate(max_deaths = max(total[stat == "deaths"], na.rm = TRUE)) %>%
  ungroup() %>%
  filter(max_deaths >= 5) %>%
  genPlotComps(geo_level = "county")
```

# Fluview

```{r}
cdcfluview::
```


## age_group_distribution
```{r}
help(age_group_distribution)
```

Age Group Distribution of Influenza Positive Tests Reported by Public Health Laboratories
Description
Retrieves the age group distribution of influenza positive tests that are reported by public health laboratories by influenza virus type and subtype/lineage. Laboratory data from multiple seasons and different age groups is provided.

Usage
age_group_distribution(years = NULL)
Arguments
years	
a vector of years to retrieve data for (i.e. 2014 for CDC flu season 2014-2015). CDC has data for this API going back to 1997. Default value (NULL) means retrieve all years. NOTE: if you happen to specify a 2-digit season value (i.e. 57 == 2017-2018) the function is smart enough to retrieve by season ID vs convert that to a year.

References
CDC FluView Portal

AGD IPT Portal

Examples
agd <- age_group_distribution(years=2015)

```{r}
cdcfluview::age_group_distribution(years = 2019) %>%
  mutate_if(is.character, as.factor) %>% summary()
```
By age
```{r}
cdcfluview::age_group_distribution(year = 2019) %>%
  group_by(age_label, wk_end) %>%
  summarise(confirmed = sum(count)) %>%
  ggplot(aes(wk_end, confirmed, color = age_label)) + geom_line()
```
By mutation
```{r}
cdcfluview::age_group_distribution(year = 2019) %>%
  group_by(vir_label, wk_end) %>%
  summarise(confirmed = sum(count)) %>%
  ggplot(aes(wk_end, confirmed, color = vir_label)) + geom_line()
```

Looks like we have postive tests data (cases) here for influenza broken out by age group and type of virus.  For purposes comparing this to Covid-19, we don't have matching age/mutation data so we'll just stick to counts by week:

```{r}
cdcfluview::age_group_distribution(year = 2019) %>%
  group_by(wk_end) %>%
  summarise(confirmed = sum(count)) %>%
  mutate(virus = "influenza") %>%
  ggplot(aes(wk_end, confirmed, color = virus)) +
  geom_line()
```

# census_regions

region/state mapping

```{r}
cdcfluview::census_regions
```
```{r}
cdcfluview::geographic_spread(years = 2019) #%>%
  mutate_if(is.character, as.factor) %>% summary()
```

```{r fig.height=8}
cdcfluview::geographic_spread(years = c(2018, 2019)) %>%
  mutate(weeks = 1) %>%
  spread(activity_estimate, weeks, fill = 0) %>%
  group_by(statename, season) %>%
  summarise_at(vars(`Local Activity`:Widespread), sum) %>%
  ungroup() %>%
  mutate(statename = fct_reorder(statename, Widespread)) %>%
  gather(spread, weeks, -statename, -season) %>%
  mutate(spread = fct_rev(fct_relevel(spread, "No Activity", "Sporadic"))) %>%
  ggplot(aes(statename, weeks, fill = spread)) +
  facet_wrap(~ season) +
  geom_bar(stat = "identity") +
  coord_flip()
```

## get_flu_data

This function has been deprecated and will be removed in future releases.
Use either ilinet() or who_nrevss() instead.

```{r}
cdcfluview::ilinet(years = c(2018, 2019), region = "state") %>%
  select(-starts_with("age"), -contains("weight")) %>%
  mutate(week_end = week_start + weeks(1)) %>%
  sample_n(10)
```

```{r}
cdcfluview::who_nrevss(years = 2018:2019, region = "state") %>%
  `$`("public_health_labs") %>% sample_n(10)
```

No dates, just state aggregates for the season.

```{r}
flu_cases <- cdcfluview::who_nrevss(years = 2017:2019, region = "state") %>%
  `$`("clinical_labs") %>% 
  mutate_at(vars(total_specimens:percent_b), as.numeric) %>%
  mutate(confirmed = total_a + total_b) %>%
  select(region, year, confirmed, total_specimens, wk_date,
         percent_positive) %>%
  gather(stat, value, confirmed, total_specimens, percent_positive)

flu_cases

flu_cases %>%
  ggplot(aes(wk_date, value, color = region)) +
  geom_line() + facet_wrap(~ stat, ncol = 1, scales = "free_y")
```

Clinical has have dates and is less biased than public health labs (public health only get positives from clinical).

## get_hosp_data

```{r}
(cdcfluview::hospitalizations(years = 2017:2019) %>%
  filter(age_label == "Overall") -> hospitalizations)
```

```{r}
hospitalizations %>%
  select(year, wk_end, rate) %>%
```


```{r}
cdcfluview::ili_weekly_activity_indicators() %>%
  filter(activity_level_label != "Insufficient Data")
```

```{r}
cdcfluview::get_weekly_flu_report()
```

## pi_mortality (deaths)

```{r}
(flu_deaths <- cdcfluview::pi_mortality(coverage_area = "state", years = 2017:2019))
```

```{r}
flu_deaths %>% mutate_if(is.character, as.factor) %>% summary()
```

```{r}
flu_deaths %>%
  select(region_name, seasonid, wk_end, number_influenza, number_pneumonia) %>%
  rename(state = region_name, date = wk_end) %>%
  group_by(seasonid) %>% 
  mutate(year = year(min(date))) %>%
  ungroup() %>%
  mutate(deaths = number_influenza + number_pneumonia) %>%
  mutate(state = paste(state, year, "flu")) %>%
  select(-starts_with("number_"), -seasonid, -year) %>%
```

```{r}
library(tidyverse)
library(lubridate)
seasons <- 2017:2019

# region: one of "national", "hhs", "census", or "state"
flu_cases_data <- cdcfluview::who_nrevss(region = "state", years = seasons) %>%
  `$`("clinical_labs")
# coverage_area: coverage area for data (national, state or region)
flu_deaths_data <- cdcfluview::pi_mortality(coverage_area = "state",
                                            years = seasons)

flu_cases_data %>%
  mutate_at(vars(total_specimens:percent_b), as.numeric) %>%
  mutate(confirmed = total_a + total_b,
         state = paste(region, year, "flu")) %>%
  select(state, confirmed, total = total_specimens, date = wk_date) %>%
  gather(stat, value, confirmed, total, confirmed) %>%
  bind_rows(
    flu_deaths_data %>%
      select(region_name, seasonid, wk_end, number_influenza, number_pneumonia) %>%
      rename(state = region_name, date = wk_end) %>%
      group_by(seasonid) %>% 
      mutate(year = year(min(date))) %>%
      ungroup() %>%
      mutate(deaths = number_influenza + number_pneumonia) %>%
      mutate(state = paste(state, year, "flu")) %>%
      select(-starts_with("number_"), -seasonid, -year) %>%
      gather(stat, value, deaths))
```


```{r}
flu_deaths_data %>%
  select(region_name, seasonid, wk_start, number_influenza, number_pneumonia) %>%
  rename(state = region_name, date = wk_start) %>%
  group_by(seasonid) %>% 
  mutate(year = year(min(date))) %>%
  ungroup() %>% select(-seasonid) %>%
  mutate(deaths = number_influenza + number_pneumonia) %>%
  #mutate(state = paste(state, year, "flu")) %>%
  select(-starts_with("number_")) %>%
  left_join(
    flu_cases_data %>%
      mutate_at(vars(total_specimens:percent_b), as.numeric) %>%
      mutate(confirmed = total_a + total_b,
             state = paste(region, year, "flu")) %>%
      select(state, date = wk_date, confirmed, total = total_specimens),
    by = c("state", "date")) %>%
  mutate(cfr = deaths/confirmed, ptr = confirmed / total) %>%
  gather(stat, total, -state, -date, -year) %>%
  left_join(
    read_csv("../data/SCPRC-EST2019-18+POP-RES.csv") %>%
      select(popM = POPESTIMATE2019, state = NAME), by = "state") %>%
  mutate(popM = if_else(state == "New York City", 8623000, popM),
         popM = (total * 1e6) / popM) %>%
  left_join(tibble(
    state = c(state.name, "District of Columbia", "New York City"),
    abb = c(state.abb, "DC", "NYC")), by = "state") %>%
  select(-state, state = abb) %>%
  mutate(state = paste(state, year, "flu")) %>%
  select(-year)
```


```{r}
fcst <- function(df, ext_days = 7, span = 1, min_days = 5) {
  has_dates <- df$date[!is.na(df$total) & !is.na(df$popM)]
  df <<- df
  if (sum(has_dates >= today() - days(min_days)) < min_days) { 
    pred_dat <- df %>% cbind(total_pred = NA, popM_pred = NA)
    return(pred_dat)
  }
  new_dates <- df$date %>% c(seq(max(., na.rm = T) + 1,
                                 max(., na.rm = T) + 1 + days(ext_days),
                                 by = "day"))
  
  ts_dat <- df %>%
    right_join(tibble(date = new_dates), by = "date")
  
  pred_dat <- ts_dat %>%
    mutate(
      total_pred = loess(total ~ as.numeric(date), data = ts_dat, span = span,
                         control = loess.control(surface = "direct")) %>%
        predict(as.numeric(new_dates)),
      popM_pred = loess(popM ~ as.numeric(date), data = ts_dat, span = span,
                         control = loess.control(surface = "direct")) %>%
        predict(as.numeric(new_dates))) %>%
    mutate_at(vars(ends_with("_pred")), function(x) {
      x[x < 0] <- 0
      for (i in 2:length(x)) {
        x[i] <- { if (x[i] < x[i - 1]) x[i - 1] else x[i] }
      }
      return(x)
    })
  return(pred_dat)
}

plot_fcst <- function(df, location = NA) {
  df %>%
    gather(type, value, popM, popM_pred, total, total_pred) %>%
    mutate(pred = endsWith(type, "_pred")) %>%
    ggplot(aes(date, value, color = type)) +
    geom_line(alpha = 0.5) + geom_point(alpha = 0.5) +
    ggtitle(location)
}

fcst_locs <- all_locs %>% 
  group_by(stat, location) %>%
  nest() %>%
  rowwise() %>%
  mutate(pred_data = list(fcst(data)))

fcst_locs %>% sample_n(1) %>%
  select(-data) %>%
  unnest(pred_data) %>% 
  select(-location) %>% plot_fcst()
```


```{r}
fcst <- function(df, ext_days = 7, span = 1, min_days = 10) {
  has_dates <- df$date[!is.na(df$total) & !is.na(df$popM)]
  df <<- df
  if (sum(has_dates >= today() - days(min_days)) < min_days) { 
    pred_dat <- df %>% cbind(total_pred = NA, popM_pred = NA)
    return(pred_dat)
  }
  new_dates <- df$date %>% c(seq(max(., na.rm = T) + 1,
                                 max(., na.rm = T) + 1 + days(ext_days),
                                 by = "day"))
  
  ts_dat <- df %>%
    right_join(tibble(date = new_dates), by = "date")
  
  pred_dat <- ts_dat %>%
    mutate(
      total_pred = loess(total ~ as.numeric(date), data = ts_dat, span = span,
                         control = loess.control(surface = "direct")) %>%
        predict(as.numeric(new_dates)),
      popM_pred = loess(popM ~ as.numeric(date), data = ts_dat, span = span,
                         control = loess.control(surface = "direct")) %>%
        predict(as.numeric(new_dates))) %>%
    mutate_at(vars(ends_with("_pred")), function(x) {
      x[x < 0] <- 0
      for (i in 2:length(x)) {
        x[i] <- { if (x[i] < x[i - 1]) x[i - 1] else x[i] }
      }
      return(x)
    })
  return(pred_dat)
}

clean_sd <- function(x) {
  sd(Filter(function(y) !is.infinite(y), x), na.rm = TRUE)
}


all_locs %>% filter(stat == "deaths") %>%
  group_by(location) %>% nest() %>%
  rowwise() %>%
  mutate(data = list(fcst(data))) %>% unnest(cols = c(data)) %>%
  group_by(location) %>%
  summarise(severity_total = suppressWarnings(
    max(total_pred, na.rm = TRUE) - max(total, na.rm = TRUE)),
            severity_popM = suppressWarnings(
              max(popM_pred, na.rm = TRUE) - max(popM, na.rm = TRUE))) %>%
  ungroup() %>%
  mutate(severity = severity_total / clean_sd(severity_total) +
         severity_popM / clean_sd(severity_popM)) %>% View()
```

