---
title: "Covid Compare analysis"
output:
  html_notebook:
    code_folding: hide
    theme: lumen
    toc: true
    toc_float: true
---

# Total counts and days to double

```{r message=FALSE, warning=FALSE}
source("../covidcomp_lib.R")
joined <- readJoinJhuData()
comp_data <- joined %>% genCompData()
comp_data %>% plotComps()
```

# Demographics

```{r}
join_wb_country <- function(df, join_data, by=c("Country/Region"="country")) {
  df %>% left_join(
    join_data %>%
      mutate(country = case_when(
        grepl("Bahamas", country) ~ "The Bahamas",
        grepl("Gambia", country) ~ "Gambia, The",
        grepl("Czech", country) ~ "Czechia",
        grepl("Iran", country) ~ "Iran",
        grepl("Ivoire", country) ~ "Cote d'Ivoire",
        grepl("Brunei", country) ~ "Brunei",
        grepl("Republic of Korea", country) ~ "Korea, South",
        grepl("Korea, Rep.", country) ~ "Korea, South",
        grepl("United Kingdom of", country) ~ "United Kingdom",
        grepl("United States", country) ~ "US",
        grepl("Viet", country) ~ "Vietnam",
        grepl("Russia", country) ~ "Russia",
        grepl("Bolivia", country) ~ "Bolivia",
        grepl("Venezuela", country) ~ "Venezuela",
        grepl("Tanzania", country) ~ "Tanzania",
        grepl("Macedonia", country) ~ "North Macedonia",
        grepl("Moldova", country) ~ "Moldova",
        grepl("Egypt", country) ~ "Egypt",
        grepl("Kyrgyz", country) ~ "Kyrgyzstan",
        grepl("Slovak", country) ~ "Slovakia",
        grepl("Vincent", country) ~ "Saint Vincent and the Grenadines",
        grepl("Lucia", country) ~ "Saint Lucia",
        grepl("Martin", country) ~ "Martinique",
        # careful with Congo
        country == "Democratic Republic of the Congo" |
          country == "Congo, Dem. Rep." ~ "Congo (Kinshasa)",
        country == "Congo" | country == "Congo, Rep." ~ "Congo (Brazzaville)",
        TRUE ~ country)),
    by = by)
}
```

## World bank population data

World bank data looks best.  Only two years old.

```{r}
library(wbstats)
demo_data <- joined %>%
  group_by(`Country/Region`) %>%
  summarise_at(vars(confirmed, deaths, recovered), max) %>%
  join_country(
    wb(indicator = "SP.POP.TOTL", startdate = 2018, enddate = 2018) %>%
      rename(population = value) %>%
      select(country, population)) %>%
  mutate(population = case_when(
    `Country/Region` == "Taiwan*" ~ 23780452,
    `Country/Region` == "Cruise Ship" ~ 3711,
    TRUE ~ population)) %>%
  join_country(
    wb(indicator = "SP.POP.65UP.TO.ZS", startdate = 2018, enddate = 2018) %>%
      rename(pct_over_65 = value) %>%
      select(country, pct_over_65)) %>%
  mutate(confirmed_pct = confirmed * 100 / population,
         deaths_pct = deaths * 100 / population,
         recovered_pct = recovered * 100 / population) %>%
  ungroup()

demo_data %>% arrange(desc(deaths_pct), desc(deaths))

demo_data %>%
  arrange(desc(deaths_pct), desc(deaths)) %>%
  head(15) %>%
  mutate(`Country/Region` = reorder(`Country/Region`, desc(deaths_pct))) %>%
  ggplot(aes(confirmed_pct, deaths_pct)) +
  geom_point(aes(color = `Country/Region`)) +
  geom_line(stat = "smooth", method = "lm", alpha = 0.2)

demo_data %>%
  arrange(desc(deaths_pct), desc(deaths)) %>%
  head(15) %>%
  mutate(`Country/Region` = reorder(`Country/Region`, desc(deaths_pct))) %>%
  ggplot(aes(pct_over_65, deaths_pct)) +
  geom_point(aes(color = `Country/Region`)) +
  geom_line(stat = "smooth", method = "lm", alpha = 0.2)

demo_data %>%
  filter(!`Country/Region` %in% c("Cruise Ship", "San Marino", "Martinique")) %>%
  arrange(desc(deaths_pct), desc(deaths)) %>%
  head(15) %>%
  mutate(`Country/Region` = reorder(`Country/Region`, desc(deaths_pct))) %>%
  ggplot(aes(confirmed_pct, deaths_pct)) +
  geom_point(aes(color = `Country/Region`)) +
  geom_line(stat = "smooth", method = "lm", alpha = 0.2)

demo_data %>%
  filter(!`Country/Region` %in% c("Cruise Ship", "San Marino", "Martinique")) %>%
  arrange(desc(deaths_pct), desc(deaths)) %>%
  head(15) %>%
  mutate(`Country/Region` = reorder(`Country/Region`, desc(deaths_pct))) %>%
  ggplot(aes(pct_over_65, deaths_pct)) +
  geom_point(aes(color = `Country/Region`)) +
  geom_line(stat = "smooth", method = "lm", alpha = 0.2)

demo_data %>%
  filter(!`Country/Region` %in% c("Cruise Ship", "San Marino", "Martinique",
                                  "Italy")) %>%
  arrange(desc(deaths_pct), desc(deaths)) %>%
  head(15) %>%
  mutate(`Country/Region` = reorder(`Country/Region`, desc(deaths_pct))) %>%
  ggplot(aes(pct_over_65, deaths_pct)) +
  geom_point(aes(color = `Country/Region`)) +
  geom_line(stat = "smooth", method = "lm", alpha = 0.2)


demo_data %>%
  filter(!`Country/Region` %in% c("Cruise Ship", "San Marino", "Martinique")) %>%
  arrange(desc(deaths_pct), desc(deaths)) %>%
  mutate(`Country/Region` = reorder(`Country/Region`, desc(deaths_pct))) %>%
  ggplot(aes(pct_over_65, deaths_pct)) +
  geom_point(aes(color = `Country/Region`)) +
  geom_line(stat = "smooth", method = "lm", alpha = 0.2) +
  theme(legend.position = "none")
```

# US State-level

```{r}
library(covid19us)
get_states_daily()

state_comp_data <- state_data %>%
  genCompData(geo_level = "Province/State", min_total = 2)
state_comp_data %>% plotComps()
```

## US State testing

```{r}
#library(rvest)
#library(magrittr)
#library(jsonlite)

(state_tests <- url("https://covidtracking.com/api/states/daily") %>%
  jsonlite::fromJSON() %>%
  mutate_at(vars(date), ymd))
```

```{r fig.height=20, fig.width=7}
state_tests %>% select(-total) %>%
  group_by(state) %>%
  summarise(
    positive_test_rate = sum(positive)/((sum(positive) + sum(negative)))) %>%
  arrange(desc(positive_test_rate))

state_tests %>% select(-total) %>%
  group_by(state) %>%
  gather(stat, value, -date, -state)  %>%
  mutate_at(vars(value), as.numeric) %>%
  ggplot(aes(date, value, fill = stat)) +
  geom_bar(stat = "identity") +
  facet_grid(vars(state), scales = "free_y")
```


```{r}
states <- state_data %>%
  left_join(state_abb_map, by = c("Province/State" = "name")) %>%
  left_join(state_tests %>%
              rename_at(vars(-date, -state), list(~ paste0(., "_tests"))),
            by = c("abb" = "state", "date"))
```


```{r fig.height=20, message=FALSE, warning=FALSE}
source("../covidcomp_lib.R")
states %>% select(-abb, -dateChecked_tests) %>%
  genCompData(geo_level = "Province/State", min_total = 2) %>%
  plotComps(min_total = 2, smooth_plots = TRUE, scale_to_fit = TRUE)
```

```{r}
jhu <- fetchPrepJhuData()
```

```{r}
source("../covidcomp_lib.R")
p <- fetchPrepJhuData() %>%
  genCompData() %>% 
  filter(location != "San Marino") %>%
  plotComps()
suppressWarnings(print(p))
```

```{r}
```

```{r}
source("../covidcomp_lib.R")
covtrack <- fetchPrepCovTrackData()
```
```{r}
p <- covtrack %>% genCompData(geo_level = "state", min_stat = "death", min_thresh = 1) %>%
  plotComps()

suppressWarnings(print(p))
```

# Corona Data Scraper project
```{r}
library(jsonlite)
cds_data <- jsonlite::fromJSON("https://coronadatascraper.com/timeseries-byLocation.json")
names(cds_data)
```

```{r}
library(tidyverse)
ita <- cds_data[["ITA"]]
names(ita)
```

```{r}
cds_data %>% head(2)
```
```{r}
sapply(cds_data, "[[", "dates") %>% unlist() %>% names() %>% gsub("^.*\\.", "", .) %>% table() 
sapply(cds_data, names) %>% unlist %>% table %>% sort
```

```{r}
library(tidyverse)
library(jsonlite)
library(lubridate)

cds_data <- jsonlite::fromJSON(
  "https://coronadatascraper.com/timeseries-byLocation.json")

valueOrNA <- function(x) {
  ifelse(!is.null(x), x, NA)
}

getTsMax <- function(cds_loc, metric) {
  suppressWarnings(max(as.numeric(sapply(
    Filter(function(y) {!is.null(y[[metric]])}, cds_loc$dates), "[[", metric))))
}

names(cds_data) %>%
  lapply(FUN = function(x) {
    list(
      name = x,
      country = valueOrNA(cds_data[[x]]$country),
      aggregate = valueOrNA(cds_data[[x]]$aggregate),
      state = valueOrNA(cds_data[[x]]$state),
      population = valueOrNA(cds_data[[x]]$population),
      county = valueOrNA(cds_data[[x]]$county),
      city = valueOrNA(cds_data[[x]]$city),
      max_deaths = getTsMax(cds_data[[x]], "deaths"),
      max_cases = getTsMax(cds_data[[x]], "cases"),
      max_tested = getTsMax(cds_data[[x]], "tested"),
      max_active = getTsMax(cds_data[[x]], "active"),
      max_recovered = getTsMax(cds_data[[x]], "recovered"),
      # deaths_ts = lapply(names(cds_data[[x]]$dates), FUN = function(x) {
      #   c(x = valueOrNA(cds_data[[x]]$dates[[x]]$deaths))
      # }),
      date = list(names(cds_data[[x]]$dates)),
      ts_values = list(cds_data[[x]]$dates))
    }) %>%
  bind_rows() %>% 
  mutate(
    max_deaths = na_if(max_deaths, -Inf),
    max_cases = na_if(max_cases, -Inf),
    max_tested = na_if(max_tested, -Inf),
    max_active = na_if(max_active, -Inf),
    max_recovered = na_if(max_recovered, -Inf)) %>%
  mutate(
    max_deaths_per_capita = max_deaths / population * 1e6,
    max_tested_per_capita = max_tested / population * 1e6,
    max_recovered_per_capita = max_recovered / population * 1e6,
    max_positive_test_rate = max_cases / max_tested) %>%
  unnest(c(date, ts_values)) %>%
  mutate(
    date = ymd(date),
    deaths = unlist(sapply(ts_values, FUN = function(x) {
      return(valueOrNA(x$deaths)) })),
    active = unlist(sapply(ts_values, FUN = function(x) {
      return(valueOrNA(x$active)) })),
    cases = unlist(sapply(ts_values, FUN = function(x) {
      return(valueOrNA(x$cases)) })),
    recovered = unlist(sapply(ts_values, FUN = function(x) {
      return(valueOrNA(x$recovered)) })),
    tested = unlist(sapply(ts_values, FUN = function(x) {
      return(valueOrNA(x$tested)) })),
    growthFactor = unlist(sapply(ts_values, FUN = function(x) {
      return(valueOrNA(x$growthFactor)) })),
    cfr = deaths / cases,
    ptr = cases / tested,
    rr = recovered / cases
    ) %>%
  select(-ts_values) %>%
  gather(stat, value, deaths, active, cases, recovered, tested,
         growthFactor, cfr, ptr, rr) %>%
  mutate(popM = value / population * 1e6) -> cds
```

# NYT data

```{r}
read_csv(url("https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-counties.csv")) %>%
  mutate(cfr = deaths / cases, county = paste(county, "County")) %>%
  mutate(state = unlist(sapply(state, FUN = function(x) { unlist(valueOrNA(state.abb[which(state.name == x)])) }))) %>%
  gather(stat, total, cases, deaths, cfr) %>%
  select(-fips) %>%
  unite(county, county, state, sep = ", ") %>%
  mutate(county = paste0(county, ", USA")) %>%
  left_join(cds %>% filter(country == "USA" & aggregate == "county") %>% select(name, population) %>% unique(), by = c("county" = "name")) %>%
  mutate(popM = total / population * 1e6) %>%
  group_by(county) %>%
  mutate(max_deaths = max(total[stat == "deaths"], na.rm = TRUE)) %>%
  ungroup() %>%
  filter(max_deaths >= 5) %>%
  genPlotComps(geo_level = "county")
```

# Fluview

```{r}
cdcfluview::
```


## age_group_distribution
```{r}
help(age_group_distribution)
```

Age Group Distribution of Influenza Positive Tests Reported by Public Health Laboratories
Description
Retrieves the age group distribution of influenza positive tests that are reported by public health laboratories by influenza virus type and subtype/lineage. Laboratory data from multiple seasons and different age groups is provided.

Usage
age_group_distribution(years = NULL)
Arguments
years	
a vector of years to retrieve data for (i.e. 2014 for CDC flu season 2014-2015). CDC has data for this API going back to 1997. Default value (NULL) means retrieve all years. NOTE: if you happen to specify a 2-digit season value (i.e. 57 == 2017-2018) the function is smart enough to retrieve by season ID vs convert that to a year.

References
CDC FluView Portal

AGD IPT Portal

Examples
agd <- age_group_distribution(years=2015)

```{r}
cdcfluview::age_group_distribution(years = 2019) %>%
  mutate_if(is.character, as.factor) %>% summary()
```
By age
```{r}
cdcfluview::age_group_distribution(year = 2019) %>%
  group_by(age_label, wk_end) %>%
  summarise(confirmed = sum(count)) %>%
  ggplot(aes(wk_end, confirmed, color = age_label)) + geom_line()
```
By mutation
```{r}
cdcfluview::age_group_distribution(year = 2019) %>%
  group_by(vir_label, wk_end) %>%
  summarise(confirmed = sum(count)) %>%
  ggplot(aes(wk_end, confirmed, color = vir_label)) + geom_line()
```

Looks like we have postive tests data (cases) here for influenza broken out by age group and type of virus.  For purposes comparing this to Covid-19, we don't have matching age/mutation data so we'll just stick to counts by week:

```{r}
cdcfluview::age_group_distribution(year = 2019) %>%
  group_by(wk_end) %>%
  summarise(confirmed = sum(count)) %>%
  mutate(virus = "influenza") %>%
  ggplot(aes(wk_end, confirmed, color = virus)) +
  geom_line()
```

# census_regions

region/state mapping

```{r}
cdcfluview::census_regions
```
```{r}
cdcfluview::geographic_spread(years = 2019) #%>%
  mutate_if(is.character, as.factor) %>% summary()
```

```{r}
cdcfluview::geographic_spread(years = 2019) %>%
  mutate(weeks = 1) %>%
  spread(activity_estimate, weeks, fill = 0) %>%
  group_by(statename) %>%
  summarise_at(vars(`Local Activity`:`Widespread`), sum) %>%
  mutate(max_widespread = max(Widespread, na.rm = TRUE)) %>%
  gather(spread, weeks, -statename, -max_widespread) %>%
  ungroup() %>%
  mutate(statename = fct_reorder(statename, max_widespread, na.rm = TRUE)) %>%
  ggplot(aes(statename, weeks, fill = spread)) + geom_bar(stat = "identity") +
  coord_flip()
```


```{r}
pi_mortality()
```
```{r}
cdcfluview::get_state_data(years = 2019)
```
```{r}
cdcfluview::surveillance_areas()
```

